---
title: "Weight of Fish"
author: "lana"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight

find the best model using two variables to predict perch weight, and compare this to the best overall model 

## Perch

```{r}
perch = filter(fish, Species == "Perch")
```


### Best Models

```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = perch)
summary(modelPerch)
```

```{r}
best2Perch = lm(Weight ~ Height + Width, data = perch)
summary(best2Perch)
```

## Best 2~variable equation 

Weight = 536 +n74.77 *height + 69.62 *width 

## Pike

```{r}
pike = filter(fish, Species == "Pike")
```


### Best Two regressor model

```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = pike)
summary(modelPike)
```

```{r}
best2Pike = lm( Weight ~ Length1 + Length2 + Length3, data = pike)
summary(best2Pike)
```

## Best 2~variable equation

weight = 1675.79 + -105.64*Length1 + 141.25*Length3

## Roach 

```{r}
Roach = filter(fish, Species == "Roach")
```

### Best Two regressor model

```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Roach)
summary(modelRoach)
```


```{r}
best2Roach = lm(Weight ~ Length1 + Length2 + Length3, data = pike)
summary(best2Roach)
```

### Best 2~variable equation

weight = -319.118 + 8.278*Length3 + 72.300* Width

## Final Summary Statements

the best model using two variables to predict perch is -536 + 74.77*Height + 69.62*Width. the best model using two variables to predict pike is weight = -1675.79 + -105.64*Length1 + 141.258*Length3. the best model using two variables to predict roach is weight = -319.118 + 8.278*Length3 + 72.300*Width 
